%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}
%\addbibresource{bibliography.bib}

\begin{document}
\header{devrin}{talen}
       {electrical engineer}

% In the aside, each new line forces a line break
\begin{aside}
  \section{about}
    57 Hunters Pointe
    Pittsford, NY 14534
    (301) 538-0091
    devrin@fastmail.com
    devrintalen.github.io
  \section{languages}
    english
    turkish
  \section{programming}
    C, Assembly
    (x86, IA64, AVR)
    Verilog
    Python, Perl
    Javascript
    (ES5, node.js)
    CSS3 \& HTML5
\end{aside}

%\section{objective}

%A full-time position in the field of computer engineering in which I can apply my skills in architecture, validation, and embedded system design. My breadth of academic background and existing industry experience make me an ideal employee in a team that focuses on getting things done.

%To obtain a full time computer engineering position in which I can apply my skills in architecture, validation, and embedded system design.

\section{education}

\begin{entrylist}
  \entry
    {2004-2008}
    {B.S. {\normalfont Electrical and Computer Engineering}}
    {Cornell University, Ithaca, NY}
    {Cum Laude, Dean's List, GPA: 3.4}
\end{entrylist}

\section{experience}

\begin{entrylist}
  \entry
    {2013--}
    {Director of Systems Engineering, Vuzix Corporation}
    {Rochester, NY}
    {Leading and managing electrical engineering team and systems design for product architecture. Experience with the design and challenges of Head-Mounted Displays and HDI PCB design. Experience with both full in-house electrical development and managing vendors. My experience spans schematic design, PCB layout, MCU firmware, Linux kernel development, FPGA RTL, and Android AOSP development.}
  \entry
    {2008--2013}
    {System Validation Engineer, Intel Corporation}
    {Hudson, MA}
    {Testing mission-critical server processors for bugs. Experience working in a lab with Tektronix logic analyzers, developing test plans, test content, and debugging system failures. Worked through multiple projects from first silicon to first sale in a variety of roles including triage and debug, RTL development, FPGA emulation, and software developer.}
  \entry
    {2007}
    {Embedded System Developer, Cornell University Satellite Team}
    {}
    {Programmed the interface boards connecting several modules to a backplane. Developed an OS driver for debugging the AVR microcontroller-based system. Team competed in the University Nanosat-4 Program.}
  \entry
    {2006--2007}
    {Co-op, Intel Corporation}
    {Hudson, MA}
    {Developed a tool to analyze the fault coverage contribution of sROSL sites on an Itanium processor design. Data generated by this tool impacted design decisions about which sROSL sites could be removed.}
    \entry
    {2005}
    {Intern, Naval Research Labs}
    {Washington, DC}
    {Performed research experiments with in a Class 4 terawatt laser facility. Responsibilities included setting up equipment, tuning optics, and carrying out experiments. Passed security clearance requirements.}
\end{entrylist}

%\section{projects}

%\begin{entrylist}
  %\entry
    %{2012}
    %{ADBUSB}
    %{}
    %{USB adapter for the 1987 Apple Extended Keyboard. Translates Apple Desktop Bus (ADB) protocol into HID-compliant USB. Developed the entire project, from the microcontroller code to the schematics to the PCB layout.}
  %% \entry
  %%   {2007}
  %%   {SIAM32: AVR USB 2.0 Host Controller}
  %%   {}
  %%   {Implemented a fully-functioning USB 2.0-compliant host controller on an Atmel Mega32 microcontroller. Coded 5,000 lines, 1,000 of which were in AVR assembly. Collaborated with two other classmates to deliver the device in under a month.}
%\end{entrylist}

\end{document}
